Assessment of the KLGO Coastal Waterbird Survey Monitoring Program

### 2019-02-16 analysis/paper/paper.Rmd
Removing ggplot caption in Survey Timing figure; correcting cache option in EDA_SurveyTiming chunk (don't cache since won't see any changes in externally sourced script).

```{r EDA_SurveyTiming, eval=TRUE, cache = TRUE, include = FALSE}
# dotplot of survey times by year
source("../scripts/survey_timing_EDA.R", echo=FALSE)

@@

```{r Fig-SurveyTiming, echo=FALSE, eval=TRUE, cache=TRUE, dependson= c("EDA_SurveyTiming"), fig.show= 'asis', fig.cap="The annual dates of the first and last survey have both varied by over a month across the years."}

>>>>

```{r EDA_SurveyTiming, eval=TRUE, cache = FALSE, include = FALSE}
# dotplot of survey times by year
source("../scripts/survey_timing_EDA.R", echo=FALSE)

@@

```{r Fig-SurveyTiming, echo=FALSE, eval=TRUE, cache=TRUE, fig.show= 'asis', fig.cap="The annual dates of the first and last survey have both varied by over a month across the years."}
